Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-27 phd/dissertation/chapter3.tex
complete point-finite and sigma-product convergence equivalence

Circumventing this takes a bit of extra bookkeeping. We proceed by defining
a simpler infinite game for each cardinal $\kappa$.

@@

\begin{proof}
  Let $\sigma$ be a coding strategy for $\pl F$ in $\pfgame\kappa$
  such that $\sigma(F,C)\supset F$.

  For $F\in[\kappa]^{<\omega}$ and $\epsilon>0$ let $U(F,\epsilon)$ be the
  open set in $\mathbb{R}^\kappa$ such that
  \[
    \pi_\alpha(U(F,\epsilon)) =
    \left\{
      \begin{array}{ll}
        (-\epsilon,\epsilon) & \alpha\in F\\
        \mathbb{R} & \alpha\not\in F
      \end{array}
    \right.
  \]
  Note that $F$ is uniquely identifible given
  $U(F,\epsilon)\cap\SigmaProdR\kappa$.

  For each point $x\in\SigmaProdR\kappa$ and $\epsilon\geq 0$, let
  $C_\epsilon(x)\in[\kappa]^{\leq\omega}$
  such that $\alpha\in C_\epsilon(\alpha)$ if and only if
  $|x(\alpha)|\geq\epsilon$.

  TODO: Finish

  % We define the coding strategy $\tau$ for $\pl O$ in
  % $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
  % \[
  %   \tau(\<U(\tau(\<U,x\>,\epsilon)\cap\SigmaProdR\kappa,x\>)
  %     =
  %   U(\sigma(\<F,C_{2^{-|F|}}(x)\>),2^{-|F|}) \cap \SigmaProdR\kappa
  % \]

  % Assume that $\pl O \not\codewin \congame{\SigmaProdR\kappa}{\vec0}$. Then
  % there exists a legal attack $a=\<a_0,a_1,\dots\>$ by $\pl P$ against $\tau$.
  % Since $a$ does not converge to $\vec0$, it follows there is some
  % $\alpha<\kappa$ such that $a_n(\alpha)$ does not converge to $0$. Thus there
  % is a sequence $n_0<n_1<\dots$ such that $|a_{n_i}(\alpha)|\geq 2^{-n_i}$, and
  % it follows that $\alpha\not\in\sigma(\<F,C_{2^{-|F|}}(x)\>)$ at any stage
  % of the game.

  % Consider the attack $a'=\<$
\end{proof}

\begin{thm}
  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
  Then $\pl F \codewin \pfgame\kappa$.
\end{thm}

\begin{proof}
Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
$W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
$W\subseteq c(\gamma_W)$.

Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.

Define the coding strategy $\sigma$ as follows:
  \[
    \sigma(\emptyset) = \emptyset
  \]
  \[
    \sigma(\<N,W\>)
      =
    N
      \cup
    (|N|+1)
      \cup
    \{\gamma_W\}
      \cup
    \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
  \]

Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
$N_0=\sigma(\emptyset)$, and
$N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
playthrough of the game coresponding to the coding strategy $\sigma$ and
attack $a$.

Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
$n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
that $\alpha\in c(\gamma_{W_i})\rest n$.
Finally, we consider
  \[
    N_{n+1}
      =
    \sigma(\<N_n,W_n\>)
      \supseteq
    \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
      \supseteq
    c(\gamma_{W_i})\rest |N_n|
  \]
and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
\end{proof}

  (TODO: The above result is cute, but unnecessary due to the below.)

>>>>

Circumventing this takes a bit of extra machinery. We proceed by defining
a simpler infinite game for each cardinal $\kappa$.

@@

\begin{proof}
  Let $\sigma$ be a winning coding strategy for $\pl F$ in $\pfgame\kappa$
  such that $\sigma(\emptyset)\supset\emptyset$ and $\sigma(F,C)\supset F$.

  For $F\in[\kappa]^{<\omega}$ and $\epsilon>0$ let $U(F,\epsilon)$ be the
  basic open set in $\mathbb{R}^\kappa$ such that each projection is of the form
  \[
    \pi_\alpha(U(F,\epsilon)) =
    \left\{
      \begin{array}{ll}
        (-\epsilon,\epsilon) & \alpha\in F\\
        \mathbb{R} & \alpha\not\in F
      \end{array}
    \right.
  \]
  Note that $F\supset\emptyset$ and $\epsilon$ are uniquely identifible given
  $U(F,\epsilon)\cap\SigmaProdR\kappa$.

  For each point $x\in\SigmaProdR\kappa$ and $\epsilon> 0$, let
  $C_\epsilon(x)\in[\kappa]^{\leq\omega}$
  such that $\alpha\in C_\epsilon(\alpha)$ if and only if
  $|x(\alpha)|\geq\epsilon$.

  We define the coding strategy $\tau$ for $\pl O$ in
  $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
  \[
    \tau(\emptyset)
      =
    U(\sigma(\emptyset),1) \cap \SigmaProdR\kappa
  \]
  \[
    \tau(\<U(F,\epsilon)\cap\SigmaProdR\kappa,x\>)
      =
    U\left(\sigma(\<F,C_{\epsilon}(x)\>),\frac{\epsilon}{2}\right)
      \cap
    \SigmaProdR\kappa
  \]

  Let $\<a_0,a_1,a_2,\dots\>$ be a legal attack by $\pl P$ against $\tau$. It
  then follows that
    \[
      b=\<C_{1}(a_0),C_{1/2}(a_1),C_{1/4}(a_2),\dots\>
    \]
  is a
  legal attack by $\pl C$ against $\sigma$. Since $\sigma$ is a winning
  strategy, each ordinal in $\bigcup_{n<\omega} C_{2^{-n}}(a_n)$ is in
  $C_{2^{-n}}(a_n)$ only for finitely many $n<\omega$. Thus for every coordinate
  $\alpha<\kappa$ it follows that there exists some $n_\alpha<\omega$ such that
  $a_{n}(\alpha)\leq 2^{-n}$ for $n\geq n_\alpha$. We conclude $a_n\to\vec0$,
  showing that $\tau$ is a winning strategy.
\end{proof}

% \begin{thm}
%   Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
%   Then $\pl F \codewin \pfgame\kappa$.
% \end{thm}

% \begin{proof}
% Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
% $W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
% $W\subseteq c(\gamma_W)$.

% Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
% $W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.

% Define the coding strategy $\sigma$ as follows:
%   \[
%     \sigma(\emptyset) = \emptyset
%   \]
%   \[
%     \sigma(\<N,W\>)
%       =
%     N
%       \cup
%     (|N|+1)
%       \cup
%     \{\gamma_W\}
%       \cup
%     \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
%   \]

% Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
% $N_0=\sigma(\emptyset)$, and
% $N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
% playthrough of the game coresponding to the coding strategy $\sigma$ and
% attack $a$.

% Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
% $n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
% that $\alpha\in c(\gamma_{W_i})\rest n$.
% Finally, we consider
%   \[
%     N_{n+1}
%       =
%     \sigma(\<N_n,W_n\>)
%       \supseteq
%     \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
%       \supseteq
%     c(\gamma_{W_i})\rest |N_n|
%   \]
% and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
% Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
% \end{proof}

%   (TODO: The above result is cute, but unnecessary due to the below.)
